Using Fundamental Measure Theory to Treat the Correlation Function of the Inhomogeneous Hard-Sphere Fluid

### 2012-08-17 papers/contact/paper.tex
added test-particle data and plotting, put data in paper.  Somethings not right scaling wise but not sure what yet Tested everything on node06.
new conclusions and remove two fixmes Tests skipped!

\fixme{Figure out whether to stick with both $R$ and $\sigma$, or move
to only $\sigma$ in the paper, which would have a certain appeal.}

\fixme{Consider eliminating $n_0$ and/or $n_A$ from the plots to make
  things cleaner.}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
We (will) have compared several functionals for the contact density of
a hard-sphere fluid with simulations.  This quantity is of particular
interest, as it plays a critical role in Statistical Associating Fluid
Theory (SAFT), which is the basis of a number of recent classical
density functionals.  We compute the contact density directly from the
White Bear version of the FMT hard-sphere functional, and find
reasonable agreement?

>>>>

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/test-particle-10}
  \caption{DFT and monte-carlo nA compared with averaged test particle data with bulk filling
    fraction of 0.1.}
  \label{fig:test-particle-10}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/test-particle-40}
  \caption{DFT and monte-carlo nA compared with averaged test particle data with bulk filling
    fraction of 0.4.}
  \label{fig:test-particle-40}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
We investigated several approximations to the contact value of the
correlation function for inhomogeneous fluid distributions
corresponding to flat walls, and both concave and convex walls.  We
defined and simulated two averages of the correlation function, an
asymmetric $A$ average centered at the location of one of the two
spheres that is in contact, and a symmetric $S$ average centered at
the point of contact of touching spheres.  For each average, we
derived a functional form from FMT, and also found an approximation
that has been used in the literature.  When compared with essentially
exact Monte Carlo simulations, the $A$ correlation function derived
from Fundamental Measure Theory in Section~\ref{sec:g-A} gives
excellent results for each surface, and at both high density and low
density.  The other three approximations that we studied all showed
significant and systematic deviations under some circumstances.  Thus,
we recommend that creators of SAFT-based classical density functionals
consider using the $g_\sigma^A$ functional defined in
Section~\ref{sec:g-A}.
